\documentclass[fontsize=11bp]{article}
\usepackage{fontspec}
\usepackage{hyphenat}
\usepackage{setspace}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
% configuration
\setlength{\parindent}{0pt}
\setmainfont{Liberation Sans}
\renewcommand{\baselinestretch}{1.5}
\renewcommand\labelitemii{o}
% document properties
\author{Edmund Wu}
\date{Dec 19, 2017}

\begin{document}
\begin{center}
  Fall Final Project

  Edmund Wu {\hyp} ewu1985@bths.edu
\end{center}

\underline{Project Overview} \newline
My project is about [applications of] Artifical Intelligence.

\underline{The Pages}
\begin{itemize}
  % \item What do each of the pages of my website do?
  \item index.html {\hyp} Home page, portal to other pages
  \item ml.html {\hyp} General information of Machine Learning, visuals?
  \item pathfinding.html {\hyp} General information of Pathfinding, A* or so
  \item rl.html {\hyp} General information of Reinforcement Learning, (Q|Deep)-Learning?
  \item implementation.html {\hyp} Explanation of the code used for the Pathfinding demo
\end{itemize}

\underline{User Interaction}
\begin{itemize}
  % \item What Javascript functionality will I put into the site?
  \item Demo of A* or some other way of doing pathfinding, such as potential fields, WebGL or p5.js?
\end{itemize}

\underline{Variables}
\begin{itemize}
  % \item What are some of the challenges I foresee?
  \item Being lazy.
\end{itemize}

\underline{Presentation}
\begin{itemize}
  \item I would not care if I had to present my website to the class but I would prefer not to.
  \begin{itemize}
    \item My presentation will consist of reading off the board and going through the pages.
  \end{itemize}
\end{itemize}

\underline{Works In Progress}
\begin{itemize}
  \item For WIP 1, I will have completed most if not all of the project.
  \item For WIP 2, I will have completed the project.
  \item For WIP 3, I will have completed{\ldots}
  \item For WIP 4, I will have completed{\ldots}
  \item For WIP 5, I will have completed{\ldots}
\end{itemize}
\pagenumbering{gobble}
\end{document}
